### 2013-05-01 inst/examples/Reed.Rmd
parameter uncertainty SDP methods added

``` {r }
f <- function (x, h, p) 
{
 sapply(x, function(x){
  	S = max(x - h, 0)
  	p[1] * S * (1 - S/p[2]) + S
  })
}
````

``` {r }
r <- 1
K <- 100
pars <- c(r, K)
````

With parameters `K` = `r K` and `r` = `r r`.

@@

``` {r  SDP_Mat}
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g, pdfn)
````

@@

``` {r  find_dp_opt }
opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
````

>>>>

``` {r }
f <- RickerAllee
K <- 10
pars <- c(2, K, 5)
````

@@

``` {r  SDP_Mat}
p <- c(.2,7.5,5)
SDP_Mat <- determine_SDP_matrix(f, p, x_grid, h_grid, sigma_g, pdfn)
````

@@

``` {r  find_dp_opt }
opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
opt$S
````
